---
title: "Real Estate Investment Report"
#output: html_document
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
   # orientation: rows
params:
    text1: NA
    pic1: NA
    text2: NA
    Unit1: NA
    Unit2: NA
    Unit3: NA
    Unit4: NA
    Unit5: NA
    Pet: NA
    Garage: NA
    Storage: NA
    Utility: NA
    Other: NA
    Principal: NA
    Interest: NA
    Taxes: NA
    Insurance: NA
    PMI: NA
    Vacancy: NA
    Capex: NA
    Mait: NA
    Repairs: NA
    Loan: NA
    Rate: NA
    Loan_term: NA
    Purchase: NA
    Rehab: NA
    Down: NA
    Closing: NA
---
<style>
.value {
        color: green;
}

.value-box {
  width: 300px;
}

.caption {
  font-weight: bold;

}
#column > pre:nth-child(5) > code{
  color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;

}

#column > pre:nth-child(6) > code{
  color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;

}

#column > pre:nth-child(7) > code{
  color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;

}

#column > pre:nth-child(8) > code{
color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;

}

#column > pre:nth-child(9) > code{
color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;

}

#column > pre:nth-child(10) > code{
color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;

}

#column > pre:nth-child(11) > code{
color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;

}

#column > pre:nth-child(14) > code{
color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;
}

#column > pre:nth-child(15) > code{
color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;
}
#column > pre:nth-child(16) > code{
color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;
}
#column > pre:nth-child(17) > code{
color: black;
  font-weight: bold;
  font-family: 'Aclonica';font-size: 18px;
}
</style>




```{r include=FALSE}
library(knitr)
knitr::opts_chunk$set(comment = NA)

```
Column
-------------------------------------

```{r,echo=FALSE,warning=FALSE,results='asis'}
writeLines(params[["text2"]])
```

```{r, results='asis',echo=FALSE,warning=FALSE} 
knitr::include_graphics(params[["pic1"]])
```

```{r, results='asis',echo=FALSE,warning=FALSE}
writeLines(params[["text1"]])
writeLines(paste("Rental Income:",
                 total_income<-params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+params$Pet+params$Garage+params$Storage+params$Utility+params$Other))

```
***
Loan Details:
```{r}
writeLines(paste("Down Payment:","$",params$Purchase*(params$Down/100)))
writeLines(paste("Total Cash Needed:","$",
                 
    
    inital_investment<-round(params$Purchase*(params$Down/100)+params$Closing+params$Rehab)))

writeLines(paste("Purchase Price:","$",params$Purchase))

writeLines(paste("Loan Amount:","$",params$Loan))

writeLines(paste("Loan Term:",params$Loan_term))

writeLines(paste("Interest Rate:",params$Rate,"%"))

```
***
Reserves:
```{r}

writeLines(paste("Vacancy:",params$Vacancy,"%"))
writeLines(paste("Repairs & Maintenance:",params$Repairs,"%"))
writeLines(paste("Capital Expenditures:",params$Capex,"%"))
writeLines(paste("Management Fees:",params$Mait,"%"))
                 
```


Column
-------------------------------------
### Total Monthly Rental Income

```{r}

total_income<-params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+params$Pet+params$Garage+params$Storage+params$Utility+params$Other


  #infoBox("Total Rental Income:",color = "green",
   #         fill = T)
  #valueBox(paste("$",total_income),"Total Income",icon = shiny::icon("dollar"))
  
```

### Total Monthly Expenses
```{r}


renderValueBox({
  total_expenses<-params$Principal+params$Interest
 valueBox(paste("$",total_expenses),"Total Monthly Expenses" ,icon =shiny::icon("fa-thumbs-up"),
           color = "green")})

```

### Total Monthly Cash Flow
```{r}

    p= params$Loan
    j=params$Rate/(12*100)
    L=params$Loan_term
    N= L*12
    
    te<-round(p*(j/(1-(1+j)^-N)),digits = 2)+params$Taxes+params$Insurance+params$PMI+
      (params$Repairs/100)*(params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+
      params$Pet+params$Garage+params$Storage+params$Utility+params$Other)+(params$Vacancy/100)*(params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+                                                                                                                  params$Pet+params$Garage+params$Storage+params$Utility+params$Other)+(params$Capex/100)*
      (params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+
         params$Pet+params$Garage+params$Storage+params$Utility+params$Other)+(params$Mait/100)*
      (params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+
         params$Pet+params$Garage+params$Storage+params$Utility+params$Other)
  
    ti<- params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+
      params$Pet+params$Garage+params$Storage+params$Utility+params$Other
    
    cf<-round((ti-te))

    
  valueBox(paste("$",cf),"Total Monthly Cash Flow" ,icon =shiny::icon("fa-thumbs-up"),
           color = "green")


```

### COCROI
```{r}
#
#    
#    p= params$Loan
#    j=params$Rate/(12*100)
#    L=params$Loan_term
#    N= L*12
#    
#    te<-round(p*(j/(1-(1+j)^-N)),digits = 2)+params$Taxes+params$Insurance+params$PMI+
#      (params$Repairs/100)*(params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+
#      params$Pet+params$Garage+params$Storage+params$Utility+params$Other)+(params$Vacancy/100)*(par#ams$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+                                      #                                                                            #params$Pet+params$Garage+params$Storage+params$Utility+params$Other)+(params$Capex/100)*
#      (params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+
#         params$Pet+params$Garage+params$Storage+params$Utility+params$Other)+(params$Mait/100)*
#      (params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+
#         params$Pet+params$Garage+params$Storage+params$Utility+params$Other)
#  
#    ti<- params$Unit1+params$Unit2+params$Unit3+params$Unit4+params$Unit5+
#      params$Pet+params$Garage+params$Storage+params$Utility+params$Other
#    
#    dp<-params$Purchase*(params$Down/100)
#    
#    total_cash<-round(params$Closing+params$Rehab+dp)
#    
#    annual_cashflow<-round((ti-te)*12)
#    
#    cashoncash<-round((annual_cashflow/total_cash)*100)
#    
#      valueBox(paste(cashoncash,"%"))
#
#    
```




